DISTRIBUTED CROSS-RELATION-BASED FREQUENCY-DOMAIN\\ BLIND SYSTEM IDENTIFICATION USING ONLINE-ADMM

### 2022-05-02 paper.tex
change abstract to distributed algorithm

\documentclass{article}
\usepackage[preprint]{spconfa4}
\usepackage{amsmath,graphicx}
\input{preamble.tex}

@@

% Title.
% ------
\title{DISTRIBUTED CROSS-RELATION-BASED FREQUENCY-DOMAIN\\ BLIND SYSTEM IDENTIFICATION USING ONLINE-ADMM}
%
% Single address.
% ---------------
\name{M. Blochberger\sthanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network. This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No. 956369. Source code available at \url{https://github.com/SOUNDS-RESEARCH/iwaenc2022-admm-bsi}.}, F. Elvander\sthanks{This work was supported in part by the Research Foundation - Flanders (FWO) grant 12ZD622N.}, R. Ali, T. van Waterschoot, M. Moonen, J. Østergaard, J. Jensen}
\address{KU Leuven\\Department of Electrical Engineering (ESAT)\\STADIUS Center for Dynamical Systems, Signal Processing and Data Analytics \\3001 Leuven, Belgium}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
    In this paper, we propose a distributed cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain using the alternating direction method of multipliers (ADMM) in a sensor network with a fusion center.
    The network consists of a fixed number of nodes each equipped with a processing unit as well as a sensor that represents an output channel of the SIMO system.
    The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into sub-problems involving a subset of channels which is determined by the network topology.
    Each network node delivers estimates for the subset of channel frequency responses, which then are communicated to the networks fusion center and combined into a consensus estimate per channel using general form consensus ADMM in an adaptive updating scheme.
    With numerical simulations, we show that it is possible to achieve convergence speeds and estimation errors comparable to low-cost frequency-domain algorithms and a high-performing Quasi-Newton algorithm.
\end{abstract}
%
\begin{keywords}
    blind system identification, multichannel signal processing, distributed signal processing, ADMM, Online-ADMM
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

@@

The alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} solves optimization problems by splitting them into smaller sub-problems, each less complex to solve than the original one.
In this paper, we use ADMM to separate the inter-channel cross-relations to form smaller sub-problems involving overlapping subsets of the entire channel set and use equality constraints to find a consensus on the overlapping estimated sub-problem parameters.
The ADMM update steps are applied in a block processing scheme forming an adaptive algorithm also referred to as Online-ADMM \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.

@@

Analogous to the time-domain formulation, the vector \(\hf\) is a stacked vector of complex-valued frequency responses.
In the presence of noise, the system of equations \eqref{eq:frequency_domain:null_space} is best solved by posing it as a least-mean-squares minimization problem \cite{guanghanxuLeastsquaresApproachBlind1995,huangAdaptiveMultichannelLeast2002}:
%  minimizing \(\|\underline{\bm{e}} \|^2 = \| \Rf \hf \|^2\) with the constraint \(\hf^\herm \hf = a\) to avoid the trivial zero solution.
% As this effectively seeks the \(a\)-scaled eigenvector of the squared hermitian matrix \(\Rf^\herm \Rf\) corresponding to the smallest eigenvalue, we can replace it with its non-squared form \(\Rf\) as the eigenvectors for both are equal.
% To compute the estimates, we minimize the cost function
% \begin{equation}
%     J(\hf)(m+1) = \hf^\herm(m) \Rf(m) \hf(m)\label{eq:frequency_domain:cost_function}
% \end{equation}
% as the minimization problem
\begin{align}
    \hat{\hf}(m+1) = \arg \min_{\hf} \quad &\hf^\herm(m) \hat{\Rf}(m) \hf(m) \label{eq:frequency_domain:min_prob}\\
    \text{s.t. } \quad &\hf^\herm(m+1) \hf(m+1) = 1.
\end{align}

>>>>

\documentclass{article}
\usepackage[preprint]{spconfa4}
\usepackage{amsmath,graphicx}
\input{preamble.tex}
\ninept

@@

% Title.
% ------
\title{DISTRIBUTED CROSS-RELATION-BASED FREQUENCY-DOMAIN\\ BLIND SYSTEM IDENTIFICATION USING ONLINE-ADMM}
%
% Single address.
% ---------------
\name{M. Blochberger\sthanks{This research work was carried out at the ESAT Laboratory of KU Leuven, in the frame of the SOUNDS European Training Network. This project has received funding from the European Union's Horizon 2020 research and innovation programme under the Marie Skłodowska-Curie grant agreement No. 956369. Source code available at \url{https://github.com/SOUNDS-RESEARCH/iwaenc2022-admm-bsi}.}, F. Elvander\sthanks{This work was supported in part by the Research Foundation - Flanders (FWO) grant 12ZD622N.}, R. Ali, T. van Waterschoot, M. Moonen, J. Østergaard, J. Jensen}
\address{KU Leuven\\Department of Electrical Engineering (ESAT)\\STADIUS Center for Dynamical Systems, Signal Processing and Data Analytics \\3001 Leuven, Belgium}
%
\begin{document}
%\ninept
%
\maketitle
%
\begin{abstract}
    In this paper, we propose a distributed cross-relation-based adaptive algorithm for blind identification of single-input multiple-output (SIMO) systems in the frequency domain using the alternating direction method of multipliers (ADMM) in a sensor network with a fusion center.
    The network consists of a fixed number of nodes each equipped with a processing unit as well as a sensor that represents an output channel of the SIMO system.
    The proposed algorithm exploits the separability of the cross-channel relations by splitting the multichannel identification problem into sub-problems involving a subset of channels which is determined by the network topology.
    Each network node delivers estimates for the subset of channel frequency responses, which then are communicated to the networks fusion center and combined into a consensus estimate per channel using general form consensus ADMM in an adaptive updating scheme.
    With numerical simulations, we show that it is possible to achieve convergence speeds and estimation errors comparable to fully centralized low-cost frequency-domain algorithms and a high-performing Quasi-Newton algorithm.
\end{abstract}
%
\begin{keywords}
    blind system identification, multichannel signal processing, distributed signal processing, ADMM, Online-ADMM
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

@@

While there exist distributed signal processing algorithms for applications such as noise cancellation \cite{}, echo control \cite{} or beamforming \cite{}, there is a gap regarding BSI which we are starting to fill with this contribution.
The general-form consensus alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} solves optimization problems with cost functions separable in its variable.
We separate the inter-channel cross-relations of the BSI problem according to the networks topology, i.e. each node

to form smaller sub-problems involving overlapping subsets of the entire channel set and use equality constraints to find a consensus on the overlapping estimated sub-problem parameters.

% The alternating direction method of multipliers (ADMM) \cite{boydDistributedOptimizationStatistical2011} solves optimization problems by splitting them into smaller sub-problems, each less complex to solve than the original one.
% In this paper, we use ADMM to separate the inter-channel cross-relations to form smaller sub-problems involving overlapping subsets of the entire channel set and use equality constraints to find a consensus on the overlapping estimated sub-problem parameters.
% The ADMM update steps are applied in a block processing scheme forming an adaptive algorithm also referred to as Online-ADMM \cite{wangOnlineAlternatingDirection2013,hosseiniOnlineDistributedADMM2014}.

@@

Analogous to the time-domain formulation, the vector \(\hf\) is a stacked vector of complex-valued frequency responses.
In the presence of noise, the system of equations \eqref{eq:frequency_domain:null_space} is best solved by posing it as a least-mean-squares minimization problem \cite{guanghanxuLeastsquaresApproachBlind1995,huangAdaptiveMultichannelLeast2002}:
%  minimizing \(\|\underline{\bm{e}} \|^2 = \| \Rf \hf \|^2\) with the constraint \(\hf^\herm \hf = a\) to avoid the trivial zero solution.
% As this effectively seeks the \(a\)-scaled eigenvector of the squared hermitian matrix \(\Rf^\herm \Rf\) corresponding to the smallest eigenvalue, we can replace it with its non-squared form \(\Rf\) as the eigenvectors for both are equal.
% To compute the estimates, we minimize the cost function
% \begin{equation}
%     J(\hf)(m+1) = \hf^\herm(m) \Rf(m) \hf(m)\label{eq:frequency_domain:cost_function}
% \end{equation}
% as the minimization problem
\begin{align}
    \hat{\hf} = \arg \min_{\hf} \quad &\hf^\herm \hat{\Rf} \hf \label{eq:frequency_domain:min_prob}\\
    \text{s.t. } \quad &\hf^\herm \hf = 1.
\end{align}
